
%!TEX root = ../article.tex

% Introduction
\section{Introduction}
\label{sec:introduction}


\IEEEPARstart{T}{his} is a well organized \LaTeX ~template for the IEEE papers that can be used by  the graduate students to prepare the IEEE conference and journal papers.



\subsection{Titles}

One can modify the author list, institution, address, correspondence email and title of paper in the file \verb+article.tex+.



\subsection{Math formula}

Some frequently used formulas can be found in the file \verb+math.tex+.
To refer a formula, use the corresponding command.
For example, we can add the Maxwell's equations as \verb+\maxwell+, and produce:

\maxwell

More formated equations are summerized  in the appendix.



\subsection{Bibliography}

We can use the Jabref software to manage the bibliography.
The file \verb+bib.bib+ can be used as a common library to add references to the manuscript.

\begin{itemize}
  \item Add BibTeX Entry: On the website (https://ieeexplore.ieee.org), click the button ``Download citations'' and choose output format ``BibTeX''. Copy the text and paste it into the file \verb+bib.bib+ by using Jabref (New BibTeX entry, BibTeX source).
  \item Merge Multiple Bibliography files: In Jabref, Import into current library, Deselect all duplicates, Save.
  \item Insert Citations: This is an example in how to cite a bibliography entry \cite{cao2018, cui2019}.
\end{itemize}

\subsection{IEEE LaTeX Analyzer}
The IEEE LaTeX Analyzer is an online service, built to assist authors with validating their LaTeX article packages. The tool provides detailed results for uploaded LaTeX packages, along with a resource for correcting any LaTeX issues, if needed. The IEEE LaTeX Analyzer can be used at any time, with one ideal use being prior to peer review article submission. Validating LaTeX article packages prior to submission helps to ensure the fastest possible speed to publication.
The website is:
\verb+http://latexqc.ieee.org/+